## Flagged Values

```{r report.flag_prep}
fig.height.flag <- 2 + num.samples * num.replicates / 6
```

### Possible PCR Stutter Removed

These tables show samples that had a candidate allele filtered out because it
was potential PCR stutter.

```{r report.stutter, fig.height=fig.height.flag}
plot_heatmap_stutter(results)
```

### Possible PCR Artifacts Removed

These tables show samples that had a candidate allele filtered out because it
was a potential (non-stutter) PCR artifact.

```{r report.artifacts, fig.height=fig.height.flag}
plot_heatmap_artifacts(results)
```

### More than Two Prominent Sequences

These tables are color-coded to show samples with more than two abundant 
sequences still present after all filtering. Cases with more than two could 
imply contamination or excessive PCR stutter or artifacts obscuring the correct
allele sequences.

```{r report.peaks, fig.height=fig.height.flag}
plot_heatmap_prominent_seqs(results)
```

### Residual Reads from Other Sequnces

These tables are color-coded by the proportion of locus-matching reads 
represented by the called alleles per sample, running from red for 0% to white 
for 100%.  The proportion is calculated for both alleles and color-coded with
the same color for both.

```{r report.prop, fig.height=fig.height.flag}
plot_heatmap_proportions(results)
```

### Possible Homozygous Samples

These tables show which samples are reported as homozygous.

```{r report.homozygous, fig.height=fig.height.flag}
plot_heatmap_homozygous(results)
```
