## Flagged Values

```{r report.flag_prep}
fig.height.flag <- 2 + num.samples * num.replicates / 6
```

### Possible PCR Stutter

```{r report.stutter, fig.height=fig.height.flag}
plot_heatmap_stutter(results)
```

### More than Two Prominent Sequences

These tables are color-coded to show samples with more than two prominent 
sequences. Cases with more than two could imply contamination or excessive
PCR stutter.

```{r report.peaks, fig.height=fig.height.flag}
plot_heatmap_prominent_seqs(results)
```

### Residual Reads from Other Sequnces

These tables are color-coded by the proportion of locus-matching reads 
represented by the called alleles per sample, running from red for 0% to white 
for 100%.  The proportion is calculated for both alleles and color-coded with
the same color for both.

```{r report.prop, fig.height=fig.height.flag}
plot_heatmap_proportions(results)
```

### Possible Homozygous Samples

```{r report.homozygous, fig.height=fig.height.flag}
plot_heatmap_homozygous(results)
```
